The Chainsmokers’ Musical Evolution

### 2024-10-12 paper/paper.qmd
fixed table issue

Energy is a crucial feature of The Chainsmokers' music, reflecting the intensity and dynamic nature of their tracks. As shown in @fig-energy, The Chainsmokers have consistently maintained high energy levels across their albums. Tracks from albums such as *Memories...Do Not Open* and *World War Joy* exhibit energy values that typically remain above 0.7, indicating the fast-paced, upbeat nature of their music. This trend is reflective of their electronic dance music (EDM) roots, where high energy is a signature element.

@@

selected_raw_data <- raw_data[, c("album_name", "album_release_date", "danceability", "energy", "acousticness", "valence")]
selected_raw_data[, 3:6] <- round(selected_raw_data[, 3:6], 2)

>>>>

Energy is a crucial feature of The Chainsmokers' music, reflecting the intensity and dynamic nature of their tracks. As shown in @fig-energy, The Chainsmokers have consistently maintained high energy levels across their albums. Tracks from albums such as *Memories...Do Not Open* and *World War Joy* exhibit energy values that typically remain above 0.5, indicating the fast-paced, upbeat nature of their music. This trend is reflective of their electronic dance music (EDM) roots, where high energy is a signature element.

@@

selected_raw_data <- raw_data[, c("album_id", "danceability", "energy", "acousticness", "valence")]
selected_raw_data[, 2:5] <- round(selected_raw_data[, 2:5], 2)
